### 2013-09-18 Publications/2013-ISBI14/01-abstract.tex
Introduction of ISBI14
Updated bibliography

Connectivity analysis on \gls*{dmri} data of the whole-brain
suffers from distortions originated by the standard 
\gls*{epi} sequences used in acquisition. These artifacts
are present at interfaces between tissues, due to the inhomogeneity
of the field derived from the discontinuity of magnetic
susceptibility. As a result, registered signal shows characteristic
geometrical deformations and signal destruction. Thus, the artifact
is a significant pitfall that limits the success of tractography 
algorithms.

@@

In this work, we use a renowned digital phantom designed
for assessing tractography algorithms and subject it to
a theoretically correct and plausible deformation. We corrected
data with several available methodologies and provide
a ranking based on the accuracy of the resulting tractographies.

>>>>

Connectivity analysis on \gls*{dmri} data of the whole-brain
suffers from distortions originated by the standard 
\gls*{epi} sequences used in acquisition. These artifacts
are present at interfaces between tissues, due to the inhomogeneity
of the field derived from the discontinuity of magnetic
susceptibility. As a result, registered signal shows characteristic
geometrical deformations and signal destruction. These artifacts
suppose a significant pitfall that limits the success of tractography 
algorithms.

@@

In this work, we use a renowned digital phantom designed
for assessing tractography algorithms, and subject it to
a ``theoretically correct'' and plausible deformation. We
corrected data back, with several available techniques 
(namely fieldmap-based, reversed encoding-based, 
registration-based). Finally, we ranked the methods 
based on the geometrical accuracy, the dropout compensation, 
and the impact on the resulting tractography.

### 2013-09-18 Publications/2013-ISBI14/02-introduction.tex
Introduction of ISBI14
Updated bibliography

This template provides authors with most of the formatting specifications needed for preparing electronic versions of their papers. All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings. Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example. Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided. The formatter will need to create these components, incorporating the applicable criteria that follow.

>>>>

In-vivo whole-brain connectivity analysis has been a
research topic of high interest for the last
5 years \cite{jones_studying_2008}. 
\Gls*{dmri} can be used to probe the
orientation of fiber bundles within the brain,
generally applying \gls*{epi} sequences.
After a signal reconstruction step, tractography
algorithms draw a map of sampled structure.
These maps can represent the actual trajectories
of fiber bundles (deterministic tractography,
\cite{basser_microstructural_2011}) or pixel-wise
probability of connection to a certain origin
(probabilistic tractography). Finally, the
information about these connections is collected
into a network matrix that can be subjected to
the so-called ``connectome analysis''.

However, such a complex workflow is prone to
flaws that have been detailedly reported 
\cite{jones_twenty-five_2010,jbabdi_tractography:_2011}.
In order to enable reliable and robust connectome
analyses of the brain, these challenging needs for
solutions must be addressed. One prominent source
of inaccuracy are the susceptibility-derived artifacts,
for which \Gls*{epi} schemes are specially sensitive.
As susceptibility changes at tissue interfaces,
so does the magnetic field. The consequence of the 
inhomogeneity of the field translates in a highly 
distorted imaged anatomy and a significant signal 
destruction of certain regions of the brain 
(e.g. the orbitofrontal lobe, for the proximity of the
air surrounding sinuses). This artifact has been
profoundly described, and a number of methodologies
have been proposed. First approaches to
retrospective correction \cite{jezzard_correction_1995},
relied on an extra \gls*{mri} acquisition (so-called
field mapping), that probes the inhomogeneity of the field.
A second theory-based breed of methodologies acquire a 
map of the \gls*{psf} of the \gls*{epi} readouts to correct 
for the artifact \cite{robson_measurement_1997}. 
Next generation of methodologies \cite{cordes_geometric_2000,
chiou_simple_2000}, make use of the acquisition of 
extra \gls*{epi} volumes 
with specific differences that enable correction, for instance
the opposed direction of the phase encoding gradients 
Finally, the last family of methodologies acquire an 
extra \gls*{t2} image, and use its anatomical correctness 
as reference to find the deformation map through nonlinear 
registration \cite{kybic_unwarping_2000,studholme_accurate_2000}.
Registration-based methods usually map
the \gls*{t2} image to the so-called baseline (B0) volume 
of \gls*{dmri}. The choice of \gls*{t2} is due to the strong
similarity of intensity distribution with the B0 of \gls*{dmri}
datasets. More recent works report extensions of the existing
techniques \cite{andersson_how_2003,holland_efficient_2010,
andersson_comprehensive_2012}, and combined approaches
\cite{zaitsev_point_2004}.

Even though aforementioned techniques for distortion correction
have been studied \cite{zeng_image_2002,wu_comparison_2008},
the lack of a gold-standard limit the possible benchmarking 
strategies. \cite{irfanoglu_effects_2012} opened the question
of the impact of the distortions on tractography. In this work,
we propose an evaluation framework using a detailed digital 
phantom designed for tractography. Using this framework,
we are able to compare several correction techniques and we
provide results related to their performance in the task
itself and their impact on subsequent tractography.

### 2013-09-18 Publications/2013-ISBI14/03-methods.tex
Introduction of ISBI14
Updated bibliography

\section{PROCEDURE FOR PAPER SUBMISSION}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. 
It may be used for A4 paper size if the paper size setting is suitably modified.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

>>>>

\section{METHODS}

\subsection{Digital Phantom}
We modified the digital phantom provided with the
\emph{\gls*{hardi} reconstruction challenge} held
in ISBI 2013, San Francisco, US. This model is
built upon high-resolution \glspl*{tpm}, from which
\gls*{dmri} signal can be simulated with different
\glspl*{snr}. The new version of the phantom includes
a \gls*{csf} distribution, which was not simulated
in the version available for the contest. For this paper,
with these new \glspl*{tpm} we produced \gls*{dti} at
typical low-resolution, and corresponding \gls*{t1} and 
\gls*{t2} images at high-resolution. All the
modalities where numerically simulated, using previously
reported \gls*{mri} typical parameters.

\begin{table}[h]
\caption{Simulated \gls*{mri} modalities}
\label{table:phantom}
\begin{center}
\begin{tabular}{c|c}
\hline
Modality & Descrition \\
\hline
\gls*{dti} & 30 directions, \\
\hline
\gls*{t1} & \\
\hline
\gls*{t2} & \\
\hline
\end{tabular}
\end{center}
\end{table}

\subsection{Theory-based synthetic distortion}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{Figure of the phantom}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Original and distorted digital phantom}
      \label{fig:label}
   \end{figure}

\subsection{Evaluation workflows}
